Collaborative Visual Analysis on the Web with RCloud

### 2015-03-31 paper.tex
intro and related work
update case study and bib
fixed fig 1 caption

\title{Social Visual Analytics: DevOps for Data Scientists}

@@

%% Uncomment below to include a teaser figure.
\teaser{
  \centering
  \includegraphics[width=.95\linewidth]{fig/teaser/teaser.pdf}
  % \vspace{-.5em}
  \caption{
    An overview of features in RCloud. RCloud was built to support an environment in which a large number of loosely-related problems in data and visual analytics are solved by a small number of \emph{hackers} and \emph{scripters}. In such a shared environment, \emph{discoverability} is also a problem. RCloud supports search, annotation, recommendation, and commenting for all notebooks, enabling an overview mode where users can \emph{browse} popular and recent analyses. When problems and data sources change constantly, deployment becomes a time sink; RCloud supports \emph{transparent and automatic} deployment of analyses as web pages and web services, allowing a seamless transition from exploratory work to production code.
  }
% \vspace{-.5em}
}

>>>>

\title{Collaborative Visual Analysis on the Web with RCloud}
% \title{Integrating Social Visual Analysis and Deployment with RCloud}
% \title{Social Visual Analytics: DevOps for Data Scientists}

@@

%% Uncomment below to include a teaser figure.
\teaser{
  \centering
  \includegraphics[width=.95\linewidth]{fig/teaser/teaser.pdf}
  % \vspace{-.5em}
  \caption{
    An overview of features in RCloud. RCloud supports an environment in which a large number of loosely-related problems in data and visual analytics are solved by a small number of \emph{hackers} and \emph{scripters}. In such a shared environment, \emph{discoverability} is a concern. RCloud supports search, annotation, recommendation, and commenting for all notebooks, and provides an overview where users can \emph{browse} popular and recent analyses. When problems and data sources change frequently, deployment can become very costly; RCloud supports \emph{transparent and automatic} deployment of analyses as web pages and web services, allowing a seamless transition from data exploration work to production web services.
  }
% \vspace{-.5em}
}
